### 2023-08-24 appendix.tex
section

We add an additional transition $s$ which reset the first two additional vector coordinate from control-state $q$.
% Transition $s$ is defined to have $r_1$ as an input and a null output.
This allows to disable the transitions of $V_1$ and to "freeze" the vector of $V_1$.
% This allows the token in $r_1$ to be removed, disabling all transitions in $T_1$ and "freezing" the marking of $P_1$.

@@

Let us now prove that $V_2$ is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$.

@@

If we can always have some vector coordinate be not zero, then we can always fire some transition to add $+1$ to the penultimate additional coordinate.
% If we can always have some $p_i$ not be zero, then we can always fire some $s_{p_i}$, putting a token in $r_2$.
In this case we can add to the first additional coordinate again and assure that all transitions are live.
% In this case we must put a token back in $r_1$ and assure that all transitions in $C_2$ are live.
We must be sure that $V_2$ is live even if $V_1$ is {\em not} live.
% We must be sure that $C_2$ is live even if $C_1$ is {\em not} live.
% This is accomplished by a transition $s'$ which  "floods" the net $C_2$ with tokens, assuring that every transition is live if a token is ever put in $r_2$. Transition $s'$ has $r_2$ as its input and every place of $C_2$ as output
This is accomplished by a transition $s'$ which arbitrarily increments every other vector coordinate 
while decrementing the penultimate one and, additionally, a transition which 
substract from the last additional vector coordinate and add to the penultimate one.

Now if $q(\textbf{0})$ is reachable from $q_0(\textbf{u})$ in $V_1$, then $V_2$ can also reach a similar
vector $q(0,0,0,\ldots, 0, 1,0,0,0)$ by executing the same sequence of transitions.
Then $s$ can freeze the $V_1$ subset,
% Now if $0$ is reachable in $R(C_1, \mu_1)$  then the net $C_2$ can also reach this marking in the place of $P_1$ by executing the same sequence of transition firings. Then $s$ can fire, freezing the $C_1$ subset.
ending up in $q(0^{d+4})$, and $V_2$ is not live.
% Since $mu(p_i) = 0$ for all $p_i \in P_1$, no transition $s_{p_i}$ with $p_i \in P_1$ can fire, and $C_2$ is dead.
Thus if $q(\textbf{0})$ is reachable then $V_2$ is not live.

{\bf Suppose that $V_2$ is not live and prove that 
$q(\textbf{0})$ is reachable in V12 ???}\\

if $V_2$ is not live, then a vector \alain{vague} is reachable in which the last two coordinate are equal to $0$ and there is no reachable vector in which either is equal to at least one.
% Conversely, if $C_2$ is not live, then a marking $\mu$ must be reachable in which  $\mu(r_2) = 0$ and there is no reachable state in which $r_2$ has a token (in particular, since we do not allow token removal from $r_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $r_2$.).
If it is not possible to have a strictly positive integer in one of the last two coordinates, then the transitions \alain{vague} are not live, and the
$d$-dimensional subset of the current vector must be zero.
% If $r_2$ has no token and cannot get any, then the transitions $s_p$ are not live, and the markings of $p$ for $p \in P_1$ must be zero. 
% Thus if $C_2$ is not live then a marking is reachable in which the marking of each $p$ in $P_1$ is zero. 
Thus if $V_2$ is not live then 
$q(\textbf{0})$ is reachable.
\end{proof}

>>>>

We add an additional transition $s$ \alain{s est d'habitude un état}
which reset the first two additional vector coordinate from control-state $q$.
% Transition $s$ is defined to have $r_1$ as an input and a null output.
This allows to disable the transitions of $V_1$ and to "freeze" the vector of $V_1$.
% This allows the token in $r_1$ to be removed, disabling all transitions in $T_1$ and "freezing" the marking of $P_1$.

@@

Let us now prove that $V_2$ is live if and only if 
$q(\textbf{0})$
is reachable from $q_0(\textbf{u})$ in $V_1$ ?????.

@@

If we can always have some vector coordinate be not zero, then we can always fire some transition to add $+1$ to the penultimate additional coordinate.
% If we can always have some $p_i$ not be zero, then we can always fire some $s_{p_i}$, putting a token in $r_2$.
In this case we can add to the first additional coordinate again and assure that all transitions are live.
% In this case we must put a token back in $r_1$ and assure that all transitions in $C_2$ are live.
We must be sure that $V_2$ is live even if $V_1$ is {\em not} live.
% We must be sure that $C_2$ is live even if $C_1$ is {\em not} live.
% This is accomplished by a transition $s'$ which  "floods" the net $C_2$ with tokens, assuring that every transition is live if a token is ever put in $r_2$. Transition $s'$ has $r_2$ as its input and every place of $C_2$ as output
This is accomplished by a transition $s'$  \alain{s' est d'habitude un état}
which arbitrarily increments every other vector coordinate 
while decrementing the penultimate one and, additionally, a transition which 
substract from the last additional vector coordinate and add to the penultimate one.

Now if $q(\textbf{0})$ is reachable from $q_0(\textbf{u})$ in $V_1$ by a sequence $\sigma$, then $V_2$ can also reach a similar
vector $q(0,0,0,\ldots, 0, 1,0,0,0)$ by executing the same sequence $\sigma$.
Then $s$ can freeze the $V_1$ subset, \alain{quel subset ?}
% Now if $0$ is reachable in $R(C_1, \mu_1)$  then the net $C_2$ can also reach this marking in the place of $P_1$ by executing the same sequence of transition firings. Then $s$ can fire, freezing the $C_1$ subset.
ending up in $q(0^{d+4})$, and $V_2$ is not live.
% Since $mu(p_i) = 0$ for all $p_i \in P_1$, no transition $s_{p_i}$ with $p_i \in P_1$ can fire, and $C_2$ is dead.
Thus if $q(\textbf{0})$ is reachable in ???? then $V_2$ is not live.

{\bf Suppose that $V_2$ is not live and prove that 
$q(\textbf{0})$ is reachable in ???}\\

if $V_2$ is not live, then a vector \alain{vague} is reachable in which the last two coordinate are equal to $0$ and there is no reachable vector in which either is equal to at least one.\alain{pas compréhensible facilement}
% Conversely, if $C_2$ is not live, then a marking $\mu$ must be reachable in which  $\mu(r_2) = 0$ and there is no reachable state in which $r_2$ has a token (in particular, since we do not allow token removal from $r_2$, the marking $\mu$ must be reached in a sequence of transitions that do not place any token in $r_2$.).
If it is not possible to have a strictly positive integer in one of the last two coordinates, then the transitions \alain{vague} are not live, and the
$d$-dimensional subset \alain{subset ou vecteur ?}
of the current vector must be zero.
% If $r_2$ has no token and cannot get any, then the transitions $s_p$ are not live, and the markings of $p$ for $p \in P_1$ must be zero. 
% Thus if $C_2$ is not live then a marking is reachable in which the marking of each $p$ in $P_1$ is zero. 
Thus if $V_2$ is not live then 
$q(\textbf{0})$ is reachable in ???.
\end{proof}
